%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------



%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Team Lead of Mobile Infrastructure | SRE} % Job title
    {Browserstack, Ltd} % Organization
    {Dublin, Ireland} % Location
    {Oct 2021 - now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented a new monitoring system which replaced old Nagios setup. It features Infra as Code style and it's very easy to manage metrics and alerts. It significantly improved our observability and reduced number of problems with machines}
        \item {Designed and implemented secrets management based on Hashicorp Vault. It made us possible to quickly rotate keys when required and reduce related problems}
        \item {Engaged in activities in analyzing and finding ways to reduce security attack surface of our machines in data-centers}
        \item {Created a design of hybrid cloud which should connect our on-premise data-centers with AWS cloud in one private network}
        \item {Created a solution to achieve zero-touch provisioning for MacOS and Linux machine. This should significantly reduce Hosting efforts and make OS upgrades much easier and faster}
      \end{cvitems}
    }

    \cventry
    {Senior Software Engineer | SRE} % Job title
    {} % Organization
    {} % Location
    {Sep 2019 - Sep 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created a new Staging environment based on MacOS and Linux virtualization. I optimized performance and achieve nearly native experience for Guest OS and devices connected to USB.}
        \item {Created a new deploy system based on Hashicorp stack. It replaced an old one based on Ansible which has a problem with consistency for machines which were offline during the deploy}
        \item {Created a universal framework for automated deployments with GitHub and Jenkins.}
        \item {Created a configuration management framework to deploy configuration values and templates in different data-centers.}
        \item {Migrated dependencies management to use code defined declarative nix language. It significantly improved deployed code consistency, developers experience and reduced Ops load}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

\begin{cvparagraph}

\textbf{Main Benefits and Contributions to Employer:}

\begin{itemize}
  \item Re-imagined deploy system and increased its throughput 10+ times, improved platform stability because of significantly better code consistency
  \item Re-imagined dependency management and improved platform stability
  \item Re-imagined configuration management and reduced Ops efforts and developers experience
  \item Re-imagined secrets management and reduced Ops efforts and improved security
  \item Re-imagined staging management and improved its utilization
  \item Re-imagined monitoring system and improved platform availability for customers
\end{itemize}

\end{cvparagraph}



