%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------



%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Cooklang – Founder/Managing Owner} % Job title
    {Innovation} % Organization
    {International} % Location
    {2020 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Poke the idea and created markup language for recipes and a parser}
        \item {Created command line tools to work with recipe files}
        \item {Created iOS application which uses the markup language}
        \item {Promoted the idea and created active open source community}
      \end{cvitems}
    }

    \cventry
    {My Quiet New Car – Founder/Managing Owner} % Job title
    {} % Organization
    {} % Location
    {2019 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Modelled user persona to identify new buyer behaviour. Designed prototypes and user experience based on Ruby-on-Rails application. Collaborated with designer and copywriter. Launch and marketing campaign.}
      \end{cvitems}
    }

    \cventry
    {Filtered – Creator/Maintainer} % Job title
    {} % Organization
    {} % Location
    {2019 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Discovered and developed an elegant Ruby gem based on a filtering approach in Ruby-on-Rails application. The gem was featured on HackerNews.}
      \end{cvitems}
    }

    \cventry
    {Aleffa – Founder/Full Stack Developer} % Job title
    {} % Organization
    {} % Location
    {2013 - 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Meta-search for holiday packages. I orchestrated an army of crawlers to solve a problem related to name reoccurrences.}
      \end{cvitems}
    }

    \cventry
    {Crossfactor – Founder/Data Science Specialist} % Job title
    {} % Organization
    {} % Location
    {2008 - 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched and applied algorithms for extracting geological features from infrared satellite images. Data pre-processing (calibration, noise elimination), processing (supervised and unsupervised classification: k-means, nearest neighbour) and post-processing data for clients.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
