%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work}{15+ years in Software Engineering}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Team Lead of Mobile Infrastructure Team | SRE} % Job title
    {Browserstack, Ltd \small{cloud-based testing platform facilitating access to 3000+ types of real devices and browsers. Over 50,000 customers in 135 countries including Microsoft, Twitter, and Airbnb.}} % Organization
    {Dublin, Ireland} % Location
    {Oct 2021 - now} % Date(s)
    {
        \textbf{Key responsibilities}
        \begin{itemize}
            \item {Provisioning, monitoring and maintaining over 2,000 Linux and MacOS machines across 9 data centers}
            \item {Developing software for \textcolor{red}{xxx} and \textcolor{red}{yyy} teams to improve developering experience}
            \item {Idetifing pain points of other teams that can be solve by our team}
            \item {Creating technical documentation and tech specs}
            \item {Conducting post-incident reviews and postmortems.Implementing action items to prevent recurrence}
            % \item {Setting and measuring team goals and metrics}
            % \item {Mentoring and coaching team members for skill and career development}
            % \item {Collaborating and aligning with other teams and stakeholders}
            % \item {Developing software to enhance product reliability, performance and availability}
            % \item {Troubleshooting and resolving support escalation and incident issues for Mobile products}
            % \item {Optimising on-call rotations and processes and following incident response and communication best practices}
            % \item {Documenting processes, procedures and learnings to share knowledge and avoid single points of failure}
            % \item {Conducting post-incident reviews and postmortems and implementing action items to prevent recurrence}
        \end{itemize}
        \textbf{Key achievements}
        \begin{itemize}
            \item {Developed a universal framework for automated deployments using GitHub and Jenkins}
            \item {Reduced security attack surface of machines in data centers by \textcolor{red}{XX\%}}
            \item {Migrated AWS EC2 services to IaC with Terraform and Kubernetes}
            \item {Migrated to a new monitoring system (Prometheus, Alertmanager, Grafana) to replace Nagios and improve observability and availability}
            \item {Designed and implemented a secrets management system based on Hashicorp Vault}
            \item {Created a design document of hybrid cloud to connect on-premise data centers with AWS cloud}
            \item {Created a solution for zero-touch provisioning for MacOS and Linux machines}
        \end{itemize}
    }

    \cventry
    {Senior Software Engineer | SRE} % Job title
    {} % Organization
    {} % Location
    {Sep 2019 - Sep 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created a new Staging environment based on MacOS and Linux virtualization. Optimised performance and achieve nearly native experience for Guest OS and devices connected to USB.}
        \item {Created a new deployment system based on Hashicorp Nomad, Consul and Vault to deploy containerised or not applications.}
        \item {Created a configuration management framework to deploy configuration values and templates in textcolor{red}{How many?} data-centers.}
        \item {Significantly improved deployed code consistency and reduced Ops load \textcolor{red}{by X\%} by migrating dependencies management to use code defined declarative nix language.}
      \end{cvitems}
    }

    \cventry
    {Principal Lead Development Engineer} % Job title
    {Meetyl Europe, Ltd \textnormal{cloud-based platform for connecting companies and investors for direct meetings online, a Silicon Valley-owned company}} % Organization
    {Limerick, Ireland} % Location
    {Jul 2017 - Apr 2019} % Date(s)
    {
        \textbf{Key responsibilities}
        \begin{itemize}
            \item {Planning engineering strategies for a department.}
            \item {Determining department goals and creating implementation plans.}
            \item {Providing expert advice to other engineers.}
            \item {Creating and managing engineering budgets.}
            \item {Implementing process improvements.}
            \item {Being in charge of the technical part of the project, as well as of sprint planning in terms of development.}
            \item {Connecting departments and coordinating development.}
            \item {Identifying issues in the production phase and system and implementing monitoring solutions to overcome those issues.}
        \end{itemize}
        \textbf{Key achievements}
        \begin{itemize}
            \item {Designed and coded a Scheduling System from backend to frontend supporting business requirements, including custom rules for invitations, recurrence, multiple time zones.}
            \item {Designed and coded a Payments System using Stripe API for running per-feature sales and supporting billing cycles, upgrades and cancellations.}
            \item {Found suitable approaches for data management by designing and implementing architectural changes including designing an API, integration between frontend and backend, modularising and componentising code.}
            \item {Mentored team members to help them to upskill and develop their talents. Included observations, pair programming, running workshops, code reviews, facilitating brainstorming sessions, providing reading recommendations.}
            \item {Reduced the average waiting time for builds from 4h to 30m and average running time from 1h to 35m without spending extra budget by planning and managing the efforts of our CI build time-optimisation.}
            \item {Reduced the round-trip time between saving code and seeing changes from over 1m to 10s by planning and managing changing frontend builds to use Bazel.}
            \item {Created services to make developers’ life easier, including a UI-kit app, a system for catching and tracing errors, automatic security audits, in- house performance monitoring and others.}
        \end{itemize}
    }

    \cvblitz
    {Senior Software Engineer} % Job title
    {Scheduling system design, permissions system design, authentication \& logins} % Achievments
    {} % Organization
    {} % Location
    {Jul 2015 - Jul 2017} % Date(s)

    \cvblitz
    {Software Engineer} % Job title
    {Test environment and code-base migration for meetings system} % Achievments
    {} % Organization
    {} % Location
    {Feb 2015 - Jul 2015} % Date(s)

%---------------------------------------------------------
    % \cvblitz
    % {Cooklang (Creator/Maintainer)} % Job title
    % {Open source Markup Language for recipes} % Achievments
    % {Innovation (selected)} % Organization
    % {International} % Location
    % {2020 - Now} % Date(s)

    % \cvblitz
    % {Filtered (Creator/Maintainer)} % Job title
    % {Open source gem to create search filters with Rails’ Active Record} % Achievments
    % {} % Organization
    % {} % Location
    % {2019} % Date(s)

    % \cvblitz
    % {Crossfactor (Founder/DS Specialist)} % Job title
    % {Data science service provider extracting geological features from satellite images} % Achievments
    % {} % Organization
    % {} % Location
    % {2008 - 2014} % Date(s)

%---------------------------------------------------------
    \cvblitz
    {Full-stack Ruby-on-rails And JS Developer} % Job title
    {Clients: Getable (\textcolor{red}{What do they do in 1 sentence}), Pulse.io (\textcolor{red}{What do they do in 1 sentence}), Trainsmart (\textcolor{red}{What do they do in 1 sentence}), Oma (\textcolor{red}{What do they do in 1 sentence})} % Achievments
    {Contractors} % Organization
    {Moscow, Russia} % Location
    {2011 - 2015} % Date(s)

    \cvblitz
    {Full-stack PHP Developer} % Job title
    {Business and e-commerce sites} % Achievments
    {} % Organization
    {} % Location
    {2006 - 2011} % Date(s)

%---------------------------------------------------------
\end{cventries}
