%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------



%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Full-stack Ruby-on-Rails and JS developer} % Job title
    {Freelance} % Organization
    {Moscow, Russia} % Location
    {2011 - 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textit{GetTable: an online restaurant reservation service} (Full Stack Developer: Rails, AngularJS, PusherJS). Made it possible for call-centre people to avoid page reload and always see updated order lists.}
        \item {\textit{Pulse.io: a service for monitoring developers’ productivity} (Full Stack Developer: Rails, AngularJS, D3JS) Implemented advanced D3JS diagrams, integrated app with third-party code analytics tools (CodeClimate, GitHub) and command-line tools (git).}
        \item {\textit{Trainsmart: a fitness web app} (Senior Front-end Developer. Stack: AngularJS). Implemented features on AngularJS and built CSS component framework tailored for the project and other reusable directive components.}
        \item {\textit{Oma: an online marketing analytics service} (Junior Full stack developer: Rails, Postgresql, MongoDB, Elasticsearch, Redis, jQuery). I transferred an old code to a new design, built Ruby and JS reusable components.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-stack PHP Developer} % Job title
    {} % Organization
    {Moscow, Russia} % Location
    {2006 - 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed 20+ business and e-commerce web sites. Based on popular systems like Magento, Bitrix, Wordpress, Joomla, Drupal.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
