%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------



%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Principal Lead Development Engineer} % Job title
    {Meetyl Europe, Ltd} % Organization
    {Limerick, Ireland} % Location
    {Jul 2017 - Apr 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and coded a Meeting System from backend to frontend supporting business requirements, including custom rules for invitations, recurrence, multiple time zones.}
        \item {Designed and coded a Payments System using Stripe API for running per-feature sales and supporting billing cycles, upgrades and cancellations.}
        \item {Explored, tested and communicated various architectural changes including designing an API, integration between frontend and backend, modularising and componentising code, finding suitable approaches for data management.}
        \item {Mentored team members to help them to upskill and develop their talents. Included observations, pair programming, running workshops, code reviews, facilitating brainstorming sessions, providing reading recommendations.}
        \item {Planned and managed the efforts of our CI build time-optimisation, reducing the average waiting time for builds from 4 hours to 30 minutes and average running time from 1 hour to 35 minutes without spending extra budget.}
        \item {Planned and managed changing frontend builds to use Bazel, reducing the round-trip time between saving code and seeing changes from over a minute to 10 seconds.}
        \item {Created services to make developers’ life easier, including a UI-kit app, a system for catching and tracing errors, automatic security audits, in- house performance monitoring and others.}
      \end{cvitems}
    }

    \cventry
    {Senior Software Engineer} % Job title
    {} % Organization
    {} % Location
    {Jul 2015 - Jul 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and coded advanced Permissions System based on custom algebra, assisting product per-feature sales.}
        \item {Designed and coded advanced secure Auths System for login, login as a person, quick login as an invitee without an account.}
        \item {Created an agent-based and ODE-based model of Meetings System for predicting user base growth.}
      \end{cvitems}
    }

    \cventry
    {Software Engineer} % Job title
    {} % Organization
    {} % Location
    {Feb 2015 - Jul 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Set up test environment allowing making major code changes easier.}
        \item {Migrated codebase from DataMapper to ActiveRecord, giving access to a wider range of external libraries and simplified codebase.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

\begin{cvparagraph}

\textbf{Main Benefits and Contributions to Employer:}

\begin{itemize}
  \item Architectural changes resulting in faster build times for new features
  \item Usage of Domain-Driven Design to reduce data inconsistency and simplifying usage for other developers
  \item An increased shared understanding of the codebase and development approaches
  \item Quicker and better feedback for developer changes
  \item Increased developer engagement leading to better code
\end{itemize}

\end{cvparagraph}



